% Created 2025-06-19 Thu 15:33
% Intended LaTeX compiler: pdflatex
\documentclass[a4paper,11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\usepackage{amsmath,amsfonts,amsthm,amssymb}
\usepackage[singlelinecheck=false]{caption}
\captionsetup[subfigure]{singlelinecheck=on, labelfont=normalfont}
\captionsetup[figure]{labelfont=it}
\usepackage{graphicx}
\usepackage{rotating}
\usepackage{enumitem}
\usepackage{setspace}
\usepackage[normalem]{ulem}
\usepackage{hyperref}
\hypersetup{
colorlinks = true,
linkcolor = blue,
filecolor = magenta,
urlcolor = cyan,
citecolor = blue
}
\usepackage{natbib}
\setcounter{secnumdepth}{3}
\author{Dante Yasui}
\date{2025-06-19}
\title{Forced Removal or Moved to Opportunity?\\\medskip
\large Labor Market and Migration Effects of Japanese Internment}
\hypersetup{
 pdfauthor={Dante Yasui},
 pdftitle={Forced Removal or Moved to Opportunity?},
 pdfkeywords={migration, economic mobility, economic history},
 pdfsubject={Job market paper manuscript},
 pdfcreator={Emacs 29.1 (Org mode 9.6.6)}, 
 pdflang={English}}
\begin{document}

\maketitle
\begin{abstract}

This is the abstract.

\end{abstract}
\setcounter{tocdepth}{3}
\tableofcontents

\section{Introduction}
\label{sec:org1bab5e6}
\subsection{Research Question}
\label{sec:org9e9f9a4}
What was the effect of internment on wage growth?
\subsection{Motivation}
\label{sec:orgf23d61b}
Different studies seem to disagree on the sign of the effect.
How to square the differences?
\begin{itemize}
\item Who was hurt more by internment? Who could adapt?
\item Mechanisms: migration, rural vs. urban, occupational change?
\end{itemize}

Why it matters: different implications for other related questions.
\begin{itemize}
\item Adaptation story is an opptimistic take on forced migration; people are resilient
\item But inequality of opportunity also matters; if only realtively men benefitted, only young benefitted, etc. matters for targetted policy
\end{itemize}
\subsection{Contributions}
\label{sec:org66a3dfb}
\begin{enumerate}
\item Synthesize different findings around internment outcomes
\item Use more data to look at heterogeneous effects
\item Model migration decision after release from camp to identify tradeoffs of forced relocation
\end{enumerate}
\section{Historical Background}
\label{sec:org46d0319}
\subsection{Immigration into US}
\label{sec:org56c03e2}
\subsubsection{Japanese Immigration}
\label{sec:org17eed17}
\subsubsection{Chinese/other immigration}
\label{sec:orga75fafd}
\subsection{World War II Policies}
\label{sec:orgff67cc6}
\subsubsection{Internment}
\label{sec:org38c97c0}
\begin{itemize}
\item Evacuation
\label{sec:orge4756c0}
\item Incarceration
\label{sec:org20c47b3}
\item Confiscation
\label{sec:orgced6a6b}
\item Release
\label{sec:orgfae82a8}
\end{itemize}
\subsubsection{Other related programs}
\label{sec:orgc1de508}
\begin{itemize}
\item Military service
\label{sec:org61c818c}
\item Bracero Program
\label{sec:org1360e02}
\end{itemize}
\section{Theoretical Model}
\label{sec:org32e4139}
\subsection{}
\label{sec:orgbd90c40}

\section{Data}
\label{sec:orge0e6caa}

\section{Empirical Model}
\label{sec:org6810156}

\section{Results}
\label{sec:org32dc177}

\section{Conclusion}
\label{sec:org0eb03e0}
\end{document}