% \input{preamble}
\documentclass[a4paper,12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\usepackage{amsmath,amsfonts,amsthm,amssymb}
\usepackage[singlelinecheck=false]{caption}
% \captionsetup[subfigure]{singlelinecheck=on, labelfont=normalfont}
\captionsetup[figure]{labelfont=it}
\usepackage{enumitem}
\usepackage{setspace}
% \onehalfspacing
\usepackage[normalem]{ulem}
% \usepackage[inner=1.0in, outer=1.0in, top=1.0in, bottom=1.0in]{geometry}
\usepackage{hyperref}
\hypersetup{
colorlinks = true,
linkcolor = blue,
filecolor = magenta,
urlcolor = cyan,
citecolor = blue
}

\usepackage{tikz}

% datasummary tables formatting
\usepackage{tabularray}
\usepackage{float}
\usepackage{graphicx}
\usepackage[normalem]{ulem}
\UseTblrLibrary{booktabs}
\UseTblrLibrary{siunitx}
\newcommand{\tinytableTabularrayUnderline}[1]{\underline{#1}}
\newcommand{\tinytableTabularrayStrikeout}[1]{\sout{#1}}
\NewTableCommand{\tinytableDefineColor}[3]{\definecolor{#1}{#2}{#3}}

% for rotating tables
\usepackage{pdflscape}
\usepackage{afterpage}
\usepackage{capt-of}% or use the larger `caption` package

% set option figon to move all tables, figures to the end
\usepackage[figoff]{figcaps}

\usepackage{natbib}
\bibliographystyle{apalike}
\defcitealias{commissiononwartimerelocationPersonalJusticeDenied1983}{(\textit{Personal Justice Denied})}

\usepackage{adjustbox}

\setcounter{secnumdepth}{3}
\author{Dante Yasui}
\date{\today}
\title{Forced Removal or Moved to Opportunity?\\\medskip
\large Labor Market and Migration Effects of Japanese Internment}
\hypersetup{
 pdfauthor={Dante Yasui},
 pdftitle={Forced Removal or Moved to Opportunity?},
 pdfkeywords={migration, economic mobility, economic history},
 pdfsubject={Job market paper manuscript},
 pdfcreator={Emacs 29.1 (Org mode 9.6.6)}, 
 pdflang={English}}
\begin{document}

\maketitle

\input{abstract}

\section{Introduction}

The forced internment of over 120,000 Japanese Americans during World War II 
stands as a stark episode of racial injustice and economic loss. 
The policy displaced individuals and families 
from their homes, businesses, and farms on the West Coast;
a forced displacement that fractured communities and interrupted lives. 
Conventional understanding rightly frames this event as a traumatic scar, 
with research documenting its detrimental effects 
on property, wealth, and psychological well-being 
\cite{commissiononwartimerelocationPersonalJusticeDenied1983}.

However, an emerging body of economic literature
presents a more complex and surprising picture. 
Despite losses of property, job opportunities, and livelihoods,
some evidence suggests that for a subset of the internee population
this forced displacement paradoxically led to upward economic mobility 
in the decades following the war
\citep{arellano-boverDisplacementDiversityMobility2022},
\citep{shoagCausalEffectPlace2016}.
This finding presents a central puzzle: 
How could a policy of forced removal and incarceration 
have created economic \textit{opportunity}? 
In this paper I examine the mechanisms through which 
internment reshaped the labor market outcomes of Japanese Americans 
and, crucially, for whom these effects were most pronounced.

I argue that, at least for some internees,
internment acted as a large-scale, "move to opportunity" experiment.
Forced relocation may have generated economic gains through two primary channels.
First, it allowed internees to escape discrimination on the West Coast,
where the anti-Japanese sentiment that originally contributed to internment
may have held back their potential post-war earnings. 
Second, the quasi-random placement of internees in camps across the interior U.S.
inadvertently moved them closer to burgeoning post-war economies, 
such as those in the Midwest and Chicago,
creating new labor market prospects that would have otherwise been inaccessible
\citep{austinEastwardPioneersJapanese2007}.

To test this hypothesis, 
I use newly available linked census data from IPUMS 
to track individuals from 1940 to 1950.
I combinine these census records with detailed War Relocation Authority (WRA) 
records on internee origins and camp assignments. 
My empirical strategy leverages the intensity of internment at the county level 
to identify its causal impact. 
By comparing the outcomes of Japanese Americans 
from counties with high internment rates to a control group of Chinese Americans
and non-West Coast Japanese who were not targeted by the policy,
I can estimate the effect of forced displacement on post-war earnings
and migration.

My analysis yields three key findings. 
First, consistent with the "moved to opportunity" hypothesis,
individuals with a higher probability of internment 
experienced a significant increase in their 1950 earnings, 
even after controlling for pre-war characteristics. 
Second, this effect was not uniform across the population; 
it was driven almost entirely by women. 
Japanese American women who were likely internees 
saw substantially larger wage gains than their non-interned peers.
This result highlights a critical intersection between forced migration 
and gender dynamics. 
Third, I find that these gains are linked to migration; 
internees were more likely to move to counties with higher median incomes.

With this paper, I hope to make contributions in the following topics.
First, I hope to add to our understanding of the long-term economic consequences 
of Japanese internment 
by analysing several potential mechanisms that may have lead to
the surprising finding that a discriminatory policy of forced resettlement
may have lead to higher labor market earnings for some.
Second, this study adds to the growing body of research using
large-scale historical panel data sets which are only recently available
advances in machine-learnings.
More broadly, it provides new evidence on the causal impact of place, 
demonstrating how a large, exogenous shock to an individual's location 
can alter their economic trajectory, 
particularly for historically marginalized groups. 
The findings shed light on the complex legacy of internment 
and the different ways in which marginalized people can adapt
in spite of discrimination and adversity.

\subsection{\label{sec:history}Historical Background}
\href{https://www.archives.gov/milestone-documents/executive-order-9066}{Executive Order 9066} 
was signed on February 19, 1942 and granted the Secretary of War the authority
to designate military areas from which civilians could be prevented access. This
order was used to target all persons of Japanese descent living in the so-called
`Exclusion Zone' which included all of California, and large areas of
Washington, Oregon, and Arizona shown in blue in Figure \ref{fig:internmentmap}.
At first, the Secretary of War Henry Stimson encouraged some families 
to relocate voluntarily from the West Coast,
but starting at the end of March 1942, 
the Wartime Civil Control Administration (WCCA) and War Relocation Authority (WRA)
were established to remove all remaining Japanese Americans to temporary
Assembly Centers which were makeshift shelters in close proximity to the
population centers where these people were living. As the more permanent WRA
Relocation Centers reached completion in May 1942, all Japanese Americans left
in the West Coast were moved from Assembly Centers to Relocation Centers by
train. This process lasted until November of 1942
(\cite{commissiononwartimerelocationPersonalJusticeDenied1983},
\cite{denshoencyclopediacontributorsResettlementDenshoEncyclopedia2020}
).

As seen in Figure \ref{fig:1940JAmap}, over 90\% of the 1940 Japanese American
population lived in areas which would become subject to relocation orders.
This population was overwhelmingly concentrated along the West Coast, 
particularly in California,
which was home to large, well-established Japanese American communities,
many of whom were engaged in farming and small businesses.
The geographic concentration of this population 
in economically vital areas near major cities and military installations 
heightened the perceived security threat,
prompting their forced relocation.

Importantly for the later identifying assumptions in my empirical methods,
there is historical anecdotal evidence to suggest that these
voluntary migrants may have been an economically selected group.
Some Japanese living in the West Coast were permitted to leave the Exclusion Zone
if they had a sponsor living in another state who was able to prove that
they had a job or educational program in that state.
Some Japanese families were able to rely on business connections.
For example, in an interview with the 
\href{https://ddr.densho.org/media/ddr-manz-1/ddr-manz-1-34-transcript-2e0e58d5a9.htm}{Densho Digital Archive},
Art Imagire recalls his mother's decision to move their family to Reno, Nevada 
because one of her former clients offered her a job as a dress-maker there 
\citep{imagireArtImagireInterview2008}.
Imagire cites his mother's value for her children's education
as an important reason for why their family was one of the few which chose,
``to drop everything and move''.
Additionally, several thousand Nisei were attending college 
when Pearl Harbor was attacked.
Many Nisei students such as Sam Naito 
were sent home from West Coast schools like the University of Oregon
during their academic term \citep{naitoSamNaitoInterview2003}.
Some, like Naito, were able to transfer to schools outside of the exclusion
zone to continue their education.

After two years of WRA camp operations, the government began to debate how to
end the evacuation orders towards the end of 1944. One statement issued on
December 9 illustrates that one of the initial goals of interment was actually
to cause a permanent shift in the Japanese American population away from the
West Coast as part of a wide-scale program of `deghettoization':
\begin{quote}
  ``One of the major WRA aims, from the beginning, has been to encourage the widest possible dispersal of evacuees throughout the Nation, and this will continue as a prime objective during the final phase of the program.''
  \hfill \citetalias[p.~234]{commissiononwartimerelocationPersonalJusticeDenied1983}
\end{quote}

To the extent to which the relocation policies described above were successful,
this period of history provides an opportunity to examine
the way that contemporary or future displaced people
may potentially adapt to new labor markets and conditions.

\subsection{Motivating Literature}\label{motivation}

Several existing studies have tried to quantify the causal effect 
of Japanese internment on long-term earnings
\citep{chinLongRunLaborMarket2005}, 
childhood health
\citep{saavedraEarlyChildhoodConditions2013, 
grossmanIntergenerationalHealthEffects2025},
and educational attainment 
\citep{saavedraSchoolQualityEducational2015}. 

On the other hand, other studies have identified surprising ways 
in which internees did better than their counterparts.
\cite{shoagCausalEffectPlace2016} examine the persistant pattern of 
internees' tendency to settle closer to their assigned camp,
and as a result find that differential exposure to more affluent areas 
lead to some internees experiencing more long-term upward mobility than others.
\cite{arellano-boverDisplacementDiversityMobility2022} finds that overall, 
interned Japanese men experienced 9-22\% higher incomes 
relative to similar Chinese and non-interned Japanese men.
He attributes this effect to a combination of information and skills transfers 
among those living in camps together, 
migration to new labor markets, and career switching
that would not have happened if internees had remained in their original homes 
on the West Coast.

These economic findings are reinforced by more qualitative evidence
voiced by the Nisei themselves
and in historical research on this period.
\cite{taylorLeavingConcentrationCamps1991}
points to the differences in the benefits of relocation between
those who left earlier in 1942-1944 through work programs or education,
and those who left in 1944 and 1945 who tended to be older
and more resistant to the government's policies.
\cite{austinEastwardPioneersJapanese2007} 
highlights the experiences of several Nisei who resettled in cities such as
Chicago, Detroit and Minneapolis.
For those who faced discrimintation on the West Coast
where anti-Japanese sentiment was more prevalent,
these new cities felt more socially welcoming
and economically promising.

Aside from the importance of understanding the losses to internees, Japanese
Internment can also serve as an interesting natural experiment through the
involuntary nature of the experiences of internees. 
A key question in previous economic literature is the extent to which 
geographic location influences economic outcomes, such as upward mobility or earnings.
It is difficult to provide an unbiased causal estimate because households usually
have a large degree of choice in where they live. Previous studies have used a
variety of empirical strategies to separate out this causal effect including
controlling for observable characteristics like education
\cite{glaeserCitiesSkills2001}, worker fixed-effects , or
through leveraging other exogenous placements of households like the Moving to
Opportunity Experiment (\cite{ludwigLongTermNeighborhoodEffects2013},
\cite{chettyEffectsExposureBetter2016}, etc). 

Related to the overal racial discrimination faced by Japanse Americans,
Chinese Americans also faced immigration barriers
\cite{chenImpactSkillBasedImmigration2015},
and discrimination
\cite{chenInstitutionalDiscriminationAssimilation2024}.

Other research points to the importance of social networks for migration choices.
\cite{munshiSocialNetworksMigration2020}
expands the standard Roy model of migration choice
\citep{royThoughtsDistributionEarnings1951}
by adding the possibility for the number of individuals in a potential migrant's
social network living in a given destination to affect their utility
of living there themselves.

% *** Expand on gender differences at this time
% to explain heterogeneity findings

\section{Data}
\subsection{Linked Census Microdata}\label{sec:data-IPUMS}

I collect economic and demographic data on the populations of interest 
from the full count decenial censuses taken in 1940 and 1950
\citep{rugglesIPUMSAncestryFull2024}.
IPUMS also provides linked individual census data up until 1950
through their Multigenerational Longitudinal Panel (MLP) project
\citep{rugglesIPUMSMultigenerationalLongitudinal2025}.
I use the links between the 1940 and 1950 full-count censuses
from version 2.0 of the MLP data provided by IPUMS.
For my main analysis sample,
I select all individuals 
whose reported race in 1940 is either Japanese or Chinese,
born before 1926 (so that they would have been of working age by World War II),
and who are not missing income or employment data in either census.
This leaves me with a linked sample of 8,136 individuals,
of which about three quarters of whom are Japanese
and one quarter are Chinese.

\input{../tables/mlp_sumstats.tex}

Table \ref{tbl:mlp_sumstats} reports summary statistics for this sample,
broken down by race.
Japanese and Chinese are similar in age,
with both groups having an average year of birth of 1904.
Within the Chinese population, men are overrepresented compared to women
with 72\% being male compared to 58\% male in the Japanese population.
The 1940 census only asked about income earned through wages and employment
in the previous year.
However, the 1950 census added additional questions about other forms of income
including income earned by respondents who earned their own businesses or farms.
OCCSCORE is a variable provided by IPUMS 
which ranks the occupations of census respondents 
by the median wage that was earned for persons with the same occupation.
Both censused asked about the number of weeks each person reported working
in the previous year,
as well as the number of hours they worked in the previous week.
Employment status for this working-age sample
is equal to one if the person reported being employed,
and equal to zero if they were unemployed or not in the labor force.
I categorize unemployed persons 
together with those who are not in the labor force
to acknowledge the fact that internees may have been discouraged from
participating in the formal labor force due to trauma or discrimination.
% insert citations here to back up this story.
Farm status in either year depends on whether the respondent's family
lived on a farm or not.
I take the county of residence reported by each linked respondent
and categorize them as a migrant over this period
if the county they report in 1940 is different from their county in 1950.

In terms of economic characteristics,
the Japanese sample started with lower wages, fewer weeks and hours worked,
lower employment rates,
and lower ranked occupations in the 1940 census compared to the Chinese sample.
However, the gap in wage income seems to decreased by 1950.
In the section \ref{sec:results}, I show evidence that 
internment itself may have caused the Japanese population to earn higher wages
over this period than they would have otherwise.
The gap in weeks worked seems to also close between these two populations,
altough the difference in hours worked and occupation score
do not seem to change between 1940 and 1950.

Migration rates for Japanese are much higher than for Chinese over this period
(35\% vs 17\%).
Most of this is likely because the majority of the Japanese population 
were interned and forcibly removed from their original 1940 counties.
However, some may be due to voluntary migration
before internment orders went into effect
or after their release from the WRA camps.

In order to determine internment status at a more granular level,
I use the distribution of internees' original counties of residence
from the 1940s camp records which I describe in the following section.

\input{../figures/group-incwage-dist.tex}

Figure \ref{fig:group-incwage-dist} shows the histograms of 
the natural log of INCWAGE,
the total earnings from wages and employement
(as opposed to earnings from self-employment, farming, etc.),
across the three different treatment groups
\footnote{see section \ref{eq:predint} for more details}
among the linked MLP sample.
The first column shows that Chinese in the control group did experience
real wage growth on average over these ten years.
The difference in the Chinese log income distribution shown here
translates into an average increase in ***

\subsection{War Relcation Authority Records}

The WRA kept detailed records of the process of relocating and incarcerating 
the West Coast Japanese population.
I use the dataset from WRA Form 26: Evacuee Summary Data in the collection of 
Records About Japanese Americans Interned During World War II 
in the National Archives.
The original paper form from which this digitized version is coded 
included each internee's name, previous address in 1942, 
the assembly center and internment camp they were assigned to,
their educational attainment, occupation, 
and demographics including sex, birth year, and birthplace.

Table \ref{tbl:wra_demog} reports a summary of the main demographic variables 
of internees compared to the full 1940 Japanese population.
Internees represented a large majority (86\%) 
of the Japanese population in the US in 1940.
Internees were representative of the population in terms of their education, 
gender composition, and country of birth.
The 65\% of internees born in the US 
represent the generation known as the ``Nisei'', 
or second generation after their parents, 
the ``Issei'', who make up most of the remaining 35\% of internees.
The average Issei was born in 1890, 
and would have been in their early 50s during internment,
while the average Nisei was born in 1927 
and would have been teenagers when they were interned.

Figure \ref{fig:internee-ages} shows the distribution 
of the age of internees at the time of the evacutation order in 1942.
This figure reveals that there was a large variation in the ages of internees 
and that the ten camps were fairly balanced on their age composition.
The most prominant age range in this figure is made up of young adults 
between the ages of 15-25. 

The WRA records also provide a matching between the county of residence of all internees to the first camp they were placed.
Table \ref{tbl:cmp-cty} groups all internees into categories of their previous address to their assigned camp.
The largest 20 counties with more than 1000 interned residents are shown broken down by each of the ten camps.

Among the main internment counties, the major West Coast urban areas of Los Angeles, Seattle, Sacramento, San Franciso, and Portland.
However, there are also a large number of internees from more rural counties in California including Fresno, San Joaquin, Placer, and Tulare.
Interned Japanese came from a variety of backgrounds shown here by the range of urban and rural counties,
and also reflected in the range of occupations held by internees.

\input{../tables/wra_demog.tex}

\section{Methods}

My goal with bringing the MLP linked census data
together with the WRA internment camp data
is to create an individual-level panel data set
which includes both those persons who are likely internees
and a control group of people who were almost certainly not interned
(and considered as untreated in the natural experiment of internment).
In a hypothetical experiment with the goal of identifying the causal effect
of forced relocation and incarceration on individual earnings,
a randomly selected set of workers could have been selected from the West Coast
and sent to random destinations in the rest of the US.
In that case, a simple comparison of earnings in the displaced group
against the earnings of the workers on the West Coast who were not interned
would return the causal effect of interest.
Although in some ways Japanese internment does resemble a natural experiment,
there are some important ways in which the way people were actually interned
played out differently than this hypothetical,
which I will address in this section to motivate the main empirical strategy.

Precisely because internment was specifically targeted based on Japanese ancestry,
assignment to treatment was non-random.
\footnote{
  There were several thousand Americans of German and Italian ancestry 
  who were also interned during this period,
  although the overall magnitude was less than the group of Japanese internees
  and much less as a proportion of the existing German and Italian immigrant 
  populations.
  }
If we simply compare interned Japanese earnings after the war
to all other occupants of the West Coast,
then our estimate of internment's effect
will be biased downwards if Japanese were already restricted from
joining certain occupations by discrimination.
One potential comparison group for  West Coast Japanese is Hawaiian Japanese,
who were a large population who were not subject to internment
for economic reasons \citep{chinLongRunLaborMarket2005}.
However, we could expect that Japanese Hawaiians
would have experienced higher growth in their earnings
compared their West Coast peers even without the effect of internment.
The Japanese population in Hawaii were more economically integrated
in especially non-agricultural occupations
and could have experienced less of the post-war anti-Japanese discrimintation.

Another potential comparison group is Japanese living in mainland states 
that were not subject to internment.
However, because such a large proportion of the mainland Japanese population
were living in either Arizona, California, Oregon, or Washington
(about 90\% of the 1940 full-count census data),
this leaves a smaller control group.
Additionally, those Japanese immigrants who had already moved East away
from the point of entry on the West Coast
were likely to already be self-selected individuals
who would have had more access to higher earning job opportunities
due to education or skills.

For the reasons above, 
I follow \cite{arellano-boverDisplacementDiversityMobility2022} 
by including Chinese Americans in my main sample
together with all mainland Japanese.
Chinese immigrants entered the US West Coast 
at a similar period as the major wave of Japanese immigration.
Japanese workers were also seen as a substitute for the cheap Chinese labor 
for work on the transcontinental railroads and in agriculture 
\citep{chenImpactSkillBasedImmigration2015}.
Chinese Americans were not included in any of the relocation 
or internment orders following Executive Order 9066,
but in the absence of internment, 
their wages and employment would likely have continued to evolve similarly 
to the West Coast Japanese population.
For these reasons, Chinese make a natural comparison group 
to recreate the counterfactual earnings outcomes interned Japanese 
would have had if they had never been interned.

Although all persons of Japanese descent living on the West Coast
were ordered to evacuate outside of the Exclusion Area
(and no Chinese persons ordered to evacuate),
the ability of some Japanese to self-evacuate
means some were able to avoid being sent to any of the ten internment camps.
The \cite{dewittjohnl.FinalReportJapanese1943} puts the number of
voluntary evacuees at 4,889.
A research design which treats all Japanese living on the West Coast in 1940
as the treatment group ignore this number
as well as any voluntary emigration by Japanese
out of the West Coast to other states.
In order to estimate a more accurate estimate of the actual
probability that any individual Japanese census respondent was a true internee,
I create a measure of predicted internee status
which uses compares the number of internees in the WRA camp records
against the number of Japanese living in each county in the 1940 census.

\subsection{Predicted Internment Status}\label{sec:data-intern}

The WRA records give a 
(nearly\footnote{Some internees were sent to prisons operated by the 
Department of Justice which were not included in the WRA records.}) 
complete list of all individuals who were interned during World War II.
Although I do not know exactly which of the Japanese individuals 
in the linked sample were those who were actually sent to internment camps,
their original location in 1940 provides a good picture of who would
be likely to be an internee.
Even in the West Coast states which were subjed to internment, 
there was a large amount of variation in the proportion of internees
out of each county's pre-existing Japanese population
as measured in the 1940 full-count census data.

Figure \ref{fig:intern_map} shows a map of all 1940 counties
shaded by the proportion of WRA internees from that county
out of the 1940 Japanese population.
Counties in dark blue had existing Japanese populations in 1940
but for which no residents appear in the internment records.
Counties in yellow had as many (or more) of their 1940 Japanese residents
appear as WRA internees.
Counties which are not shaded did not have any 1940 Japanese residents.

\input{../figures/pr_interned_map.tex}

The Exclusion Zone is clearly shown in this map
by the clustering of highly-interned counties in the Southern half of Arizona,
California, and the Western halfs of both Oregon and Washington.
However, based on the comparison between the 1940 census and the WRA records,
it seems like not all counties within the Exclusion Area 
were affected equally.
For example, in San Louis Obisbo County, California,
only 439 of the county's 932 Japanese residents in 1940
ended up in the camp lists.
There are also a few counties outside of the official Exclusion Zone
from which a few internees arrived from
including Curry, New Mexico; Box Elder, Utah; and New York, New York.
This is likely due to either family reunification
or migration from those counties prior to 1942 into the West Coast.

The discrepancy between 1940 Japanese residents and internee origins
could be due to a few reasons.
General demographic changes such as births and deaths
could mean that not everyone who responded to the census was still alive in 1942
or that some children who show up in the internment camps were yet to be born in 1940.
voluntary migration could affect these interned proportions.
Some may have migrated between counties before Pearl Harbor,
or even have chosen to move outside of the Exclusion Zone
during the period when voluntary migration was encouraged by the Army.
If inter-county migration within the West Coast was widespread during this period,
that could mean that some West Coast Japanese who are identified as internees
based on their 1940 county
were actually able to escape the WRA camps.
In this case, it might be more appropriate to interpret the effect of
the predicited internment status estimated here
as the effect of evacuation orders for Japanese overall,
including migration by those who were not actually interned.

% If I move from county A to county B in 1941 and show up in wra from B,
% then I look like I get the treatment effect from county B, not county A

% If the county-level internment proportion is interpreted as 
% effect of forced migration and not camps,
% then voluntary migration outside of the excl zone that was caused by 
% EC9066 doesn't affect causal estimate.
% But if this doesn't matter for causal story,
% then why use county-level stats at all?
% We could just use the evacuation zone as an indicator
% That would treat all west coast Japanese as equally treated.
% Unless we think that voluntary migrants would get a
% different effect of internement than internees

% mention that linked sample doesn't include people who died or left US altogether

Some counties have a proportion greater than one when calculated this way.
For example, one of the thirty counties affected by this is 
Sacramento County in California 
which had a Japanese population of 6,851 in the 1940 census
but in the WRA records there are 7,827 internees who are reported
as coming from Sacramento County.
Although I use this proportion as a measure of internment status
for the linked individuals from each affected county,
it is important to note that this internment status is not a true probability.

% Identifying assumptions
The method of using county-level internment proportions
as a proxy for an individual Japanese worker's own internment status
makes the identifying assumption that
Japanese within the same county had equal chances of being interned.
This would be violated some types of workers were able to avoid internment
for reasons endogenous to their labor market outcomes.
As I discuss in section \ref{sec:history},
voluntary evacuees did anecdotally seem to be more likely relocate
for educational reasons,
or because of family and social networks living out East.
If the types of Japanese who were more likely to be able to voluntarily evacuate
were also more likely to earn higher wages,
then the estimated effect of internment on post-war earnings will
be biased upwards.

To account for this possibility,
I also include an internment status for the linked MLP sample
using the method described in 
\cite{arellano-boverDisplacementDiversityMobility2022}
which conditions on additional demographic variables.
Per his application of Bayes' Rule, 
the probability that an individual $i$ 
in the demographic group $z$ who lived in county $c$ in 1942 was interned
($Pr(I_{i}=1|z_i,c_{i})$)
could be determined from the proportion of the whole population who were interned 
($Pr(I_{i}=1)$,
the proportion of the population with demographics $z$ 
who lived in county $c$ in 1942 ($Pr(z_i,c_{i}^{1942})$),
and the probability of a known internee 
having the same demographics and county in 1942 
($Pr(z_i,c_i^{42}|I_i=1)$).

$$
Pr(I_i=1|z_i,c_i^{42}) = 
\frac{Pr(z_i,c_i^{42}|I_i=1) \cdot Pr(I_i=1)}{Pr(z_i,c_i^{42})}
$$

However, because my target sample of census respondents 
were only asked about their county of residence in the year of the census 
and not in 1942, $c_i^{1940}$ is used as a proxy 
for census respondents' 1942 locations.

The estimator for the true internment status of a census respondent is:

\begin{equation}\label{eq:predint}
\hat{E}[I]_{zc} =
\frac{n(i | z_i=z, ~ c_{i}^{42}=c)}{n(j | z_j=z, ~ c_{j}^{40}=c)}
\end{equation}

This will produce a biased estimate of true internment status if there were unobserved changes in population in each county between 1940 and 1942. For example, for a county that experienced a net outflow of residents, then the ratio of residents in 1940 vs 1942 would be greater than 1 and we would have an estimated internment probability that overstates the likelihood of anyone who lived in that county in 1940 would be interned.

\subsection{Internment's Effect on Earnings}\label{sec:wage-reg}

To measure the effect of internment on earnings, my main analysis follows the following specification.

\begin{equation}\label{eq:mainreg}
  Y_i = \alpha_i + \beta Pr(I)_c + \mathbb{X}_i \Gamma + \epsilon_i
\end{equation}

The main outcome of interest which I use for $Y_i$ is the reported dollar earnings of individual $i$ in the 1950 census.
$\alpha_i$ represent the state fixed effects for the state in which individual $i$ is living in 1950.
The vector of individual-level controls in $\mathbb{X}$ include age, sex, and individual $i$'s earnings from the 1940 census,
adjusted to 1950 dollars.

The probability of individual $i$ being an internee, $Pr(I)_i$,
is replaced by my estimated version from equation \ref{eq:predint}
using individual $i$'s reported race in 1940 as the only demographic $z$.
The main causal effect of interest is represented by the estimator $\beta$,
which represents the number of dollars of income which an individual is estimated to have gained (or lost)
when going from a non-internee to a likely internee.

A traditional difference-in-differences approach would require the
identifying assumption that both treated and untreated groups
would experience parallel trends in earnings in the absence of internment.
However, if individuals who had pre-existing advantages in the labor market
were able to self-select out of internment through voluntary migration,
then this parallel trends assumption would be violated.
By directly controlling for pre-internment income for each linked individual,
I address this concern for the variables that I do observe consistently
across censuses.

While this empirical strategy does not control 
for all time-invariant unobservable factors,
the historical evidence suggests that
observables like geographic location, education, and pre-war earnings
were the primary factors that determined the ways in which
internment and evacuation policies were individually enforced.

\section{Results}\label{sec:results}
In this section I report the outcomes from the main linked sample
described in section \ref{sec:data-IPUMS} 
on estimated coefficients from section \ref{sec:wage-reg}.

\input{../tables/reg1_tbl.tex}

Table \ref{tbl:reg1} presents the correlation between my predicted internment status and income in 1950.
All income amounts are reported in 1950 dollars.
Column (1) shows that on average, internees incomes were 42 dollars lower than non-internees 
but that this effect is not statitstically significant at the 10\% confidence level.
However, there is reason to believe that this estimate does not reflect the true causal effect of internment on later earnings.
For example, the Japanese living outside of the West Coast may have already been a group that was self-selected for higher income mobility.
Additionally, if Japanese experienced higher post-war descrimination than Chinese during this period,
then this correlation will be a downward-biased estimate of the true effect of internment status itself when comparing to the 
mostly Chinese control group.

To address these concerns, columns (2) through (4) 
add in additional controls from equation \ref{eq:mainreg}.
When I include demographic controls in column (2) 
including respondent's sex, race, and a quadratic in age,
the coefficient on the predicted internment status increases 
to a statistically significant positive effect of \$234.
At the average 1950 wage for Japanese of \$1,004, 
this represents about a 20\% increase in wages by internees,
relative to their counterfactual outcomes.
Because Japanese and Chinse populations were similar in age and sex
distributions at this time,
this seems to provide evidence that the differences in labor market 
discrimination between Japanese and Chinese in 1950
is causing a difference in the correlation in column (1) 
and the coefficient on internment status in column (2).

Column (3) includes additional controls for an individual's 
pre-internmnet income and their level of education.
While the main coefficient on internment status remains similar,
a Wald test rejects the null hypothesis
that the coefficient on 1940 income is zero
at the 95\% confidence level.
By controlling for an individual census respondent's level of income
prior to any internment policies,
this specification helps to address potential concerns
that higher-earning Japanese who were living on the West Coast in 1940
may have had an easier time escaping internment through voluntary migration
but would appear as treated based on their original 1940 county of residence.

Within the West Coast states, 
the majority of the Japanese population lived in California in 1940.
It is possible that due to selection or ethnic enclave effects 
\citep{edinEthnicEnclavesEconomic2003},
Californian internees may have experienced higher income growth
compared to internees from Arizona, Oregon, or Washington.
Column (4) adds in fixed-effects to account for internees' wage effects to
differ by their state of residence in 1950.
After allowing for internees coming from different states
to have different intercepts in equation \ref{eq:mainreg},
I can no longer reject the null hypothesis that 
internees from with higher internment proportions within the same state
experienced any significantly higher wages in 1950 
than those from less intensively interned counties.

\subsection{Alternative Internment Measures}

Table \ref{tbl:reg_altint} shows the estimates of equation \ref{eq:mainreg}
using three additional estimating methods for $\hat{E}[I_i]$.
These methods condition on different subsets of the variables
$state$ or $county$ of individual $i$ in 1940;
as well as their birthyear, $byr$; birthplace, $bpl$; $sex$; and $race$.

\input{../tables/reg_altint.tex}

Column (1) reports the same estimate as the main regression result
in table \ref{tbl:reg1} using $\hat{E}[I|county, race]$
as the estimated internment status conditional on county of residence and race.
Column (2) removes $race$ as a variable to predict internment,
applies the county-level ratio of internees to 1940 Japanese population
for both the Japanese and Chinese residents of each county.
Although the estimate of $\hat{E}[I]$ on Income in 1950 
is much larger in magnitude than the equivalent estimate in Column (1),
the standard error on this estimate is also much larger
such that we cannot reject the null that county-level internment proportion alone
has a positive effect on income.
Because this county internment proportion
does not seem to explain the any significant gap in income
when separately conditioning on individual race,
there seems to be evidence that the intersection of Japanese individuals
coming from more highly interned counties is in fact a relevant factor.
This evidence seems to contradict the possibility that something about the
highly interned counties themselves was also benefitting the Chinese individuals
who came from those counties.

Column (3) is the internment probability used by \cite{arellano-boverDisplacementDiversityMobility2022},
and instead of $county\times race$ level internment status,
it uses $\textbf{state}$ level internment proportions
together with birthplace and birthyear categories of internees
to predict individual internment status.
Although the estimate of internment on income is slightly larger here
than in column (1),
The overall magnitude and level of significance is similar.
In column (4), when conditioned on county and the full set of demographics,
the estimated effect $\hat{\beta}$  is slightly lower,
but again of similar magnitude and significance level.

By comparing column (1) to column (3) and (4),
there does not appear to be much additional explanatory power gained 
by including additional demographic factors in $\hat{E}[I]$ besides race.

For these reasons, I use $\hat{E}[I|county, race]$
as the predicted internment status in the other empirical specifications
in this paper.


\subsection{Difference-in-difference estimates}

Table \ref{tbl:regdid} shows the difference-in-difference estimates
from a regression with the general formula:

\begin{align}\label{eq:didreg}
  Y_i & = \beta_0 + \beta_1 \hat{E}[I_i]\times\mathbb{I}(YEAR=1950)  \\
      & + \beta_2\mathbb{I}(YEAR=1950) + \mathbb{X}_i \Gamma + \epsilon_i
\end{align}

Because the year fixed-

\input{../tables/regAB.tex}

\subsection{Mechanisms}

Due to the surprising nature of the result above 
that interned Japanese experienced higher incomes in 1950,
in the following sections I examine some of the potential mechanisms
that might have contributed to the main finding.

\subsubsection{Occupation and employment}

One explanation for internment having a seemingly positive effect on income
is that Japanese internees who lost saving or property may have adapted
by increasing their participation in formal labor that paid wages
(instead of earnings from working their own farms, businesses, etc).

Table \ref{tbl:reg2} reports the estimated effects of internment status
on an indicator of whether an individual was employed in 1950,
the number of hours they reported working last week,
the number of weeks worked in last year,
an occupational ranking based on the median earnings in their reported occupation category,
and an indicator for whether or not they reported a different occupation from their 1940 one.

\input{../tables/reg2_tbl.tex}

Despite their higher earnings, 
internees in this sample were less likely to be employed,
and worked fewer hours and fewer weeks than their non-interned comparison group.
Conditional on demographics and 1940 levels of these outcomes,
the coefficients in table \ref{tbl:reg2} are not significantly different than zero.
However, the direction of these coefficients 
does not help to explain the positive result in incomes.

Another potential explanation for the higher incomes of internees
could be that Japanese experienced labor market frictions
that kept them in lower earning occupations or labor markets,
which they were able to overcome after they had been
forcibly displaced.

Despite previous evidence from \cite{arellano-boverDisplacementDiversityMobility2022}
showing that by 1952 internees were more likely to have changed occupations,
the results for the linked census data shown in \ref{tbl:reg2}
indicate that instead internees were less likely to have changed occupations
between 1940 and 1950.
This may be due to differences in the self-reported nature of the JARP data,
or because internees took longer than 5-6 years after their release
to actually find those new occupations.

Column (4) reports the results from the regression of the OCCSCORE variable,
constructed by IPUMS to measure the median income of census respondents
in the same occupation category.
For those internees who did have a different occupation in 1950 than in 1940,
column (5) shows that their new occupations tended to be categorized
as lower-earning based on this OCCSCORE variable.

While the linked census data do not show evidence of internees
adapting through new individual labor market choices,
the next section show results that highlight the potential importance of the
specific counties that internees relocated to after internment
towards explaining their higher earnings.

\subsubsection{Migration}

Besides the incarceration of West Coast Japanese in the WRA camps,
a major effect of the policy of internment was the relocation of these people
away from their previous homes on the West Coast and to new counties
where they otherwise would not have chosen to move.

\input{../tables/reg3_tbl.tex}

Table \ref{tbl:reg3} reports the results for migration outcomes within the
linked sample,
controlling for demographics and 1940 levels of income.
Likely internees were about 16\% more likely than non-internees
to be living in a different county than their residence in 1940.
Column (1) shows that internment status is a statistically significant predictor 
in a logistic regression
of the probability that someone has experienced a change in county
when conditioning on demographics and 1940 income.

Columns (2) through (4) further restrict the sample to only those whose
1950 county is different than their 1940 county and report results on various
outcomes of the county that each migrants 1950 destination county.
All county-level measures are estimated using 1940 levels 
to avoid simultanaeity bias caused by the migrants in this sample affecting
the labor markets of their destinations.

Column (2) estimates the effect of internment status on the 
In this subsample, migrant internees move to counties 
with 25\% higher median incomes than non-internee migrants.
This translates to a difference of about \$140 in the median county income
measured in 1950 dollar amounts.

Column (3) estimates the effect of internment status on the log of population
of each linked migrant's destination county.
Based on this estimate, internees moved to larger population centers
than their non-interned counterparts.
The dependent variable of column (4) is the ratio of each county's 1940
population who were Japanese.
This estimate indicates that the counties which internees moved to 
had 1.3\% larger pre-existing Japanese populations 
than the counties which non-internees moved to.
Considering the fact that the average county in 1940 
had less than 1\% of its population as Japanese implies that
despite the Army's attempts at breaking up the Japanese population
\citetalias{commissiononwartimerelocationPersonalJusticeDenied1983},
internees still had the tendency to settle 
in the some of the same ethnic enclaves that had existed prior to the war.

\subsection{Heterogeneous outcomes by sex}

In this section, I examine the ways in which the consequences of internment
were experienced differently by men vs women.

% Move this section to data?
Figure \ref{fig:wageeffect} shows the scatterplot of the wage incomes
in both census years by different sub-samples.
Each dot in each panel is one observation from an individual in the main sample.
Individuals are categorized by their race and sex,
with the first row including all Japanese and the second row all Chinese.
The first column includes all women and the second column all men.
Income is reported for each group across the two census years 1940 and 1950.
The y-axis is in log scale.
Darker dots in the Japanese panels represent those individuals
with a higher predicted probability of internment.

Overall, wages increase for all groups between 1940 and 1950.
However, wages seem to increase by more for the Japanese men and women than
the Chinese men and women in this sample.

\input{../figures/wageeffect.tex}

Table \ref{tbl:reghet} shows the results of \ref{eq:mainreg}
broken down into separate subsamples.
Without accounting for sex at all in the original sample,
the effect of internment appears negative and statistically insignificant.
Columns (2) and (3) separate out this sample into men and women, respectively.
In the sample with only Japanese and Chinese men, 
there does not appear to be a significant effect of internment status on 1950 income.
However, for the sample with Japanese and Chinese women,
this effect is positive and significant at the 1\% significance level.

These results seem to suggest that even though my earlier regressions
controlled for sex on the right-hand side,
it may be that internee women were driving the earlier results.
This is surprising, but as shown in figure \ref{fig:wageeffect},
both Japanese and Chinese women seem to have experienced increases in earnings
over this period.
This is potentially because of increased labor force participation by women
during World War II carrying over to 1950.
Even considering this broad pattern,
Japanese internee women still seem to do better than other women in this sample.

Columns (4) and (5) further restrict the sample to only Japanese men
and Japanese women.
The internment status coefficient for men remains insignificant,
but the coefficient for women is even larger.
Because this sample is smaller than the overall sample,
there are fewer observations with which to estimate the main coefficient.
Despite the lower power, the positive estimated effect for Japanese women remains higher.

If Japanese experienced different levels of discrimination 
than Chinese after the war,
then it might be possible that in the regressions 
which include them in the control group,
the coefficient on internment status is biased downwards.
By only including Japanese in columns (4) and (5),
the control group is only those Japanese 
who lived in counties unaffected by internment
and who would have experienced arguably similar levels of discrimination
as the interned Japanese.

\input{../tables/reghet_tbl.tex}

\section{Conclusion}



By linking newly available 1940-1950 census data with War Relocation Authority records,
I constructed a measure of the predicted probability of internment and compared post-war outcomes for Japanese Americans against a control group of Chinese Americans.
With newly available linked 1940-1950 census data,
I sought to answer a puzzle posed by the case of Japanese internment:
how could the forced internment have paradoxically led to economic opportunity for some?
My results agree with surprising finding thata higher probability of internment
is associated with higher individual earnings in 1950, after resettlement had occured.
However, this aggregate effect masks a critical source of heterogeneity;
the gains were driven almost entirely by women.
While likely internees were more likely to migrate to higher-income and urban counties,
this channel only partially explains the results.
This could suggest that internment fundamentally altered the labor market trajectories of women
in ways not captured by simple occupational changes.

These findings build on a growing literature
that re-evaluates the long-run economic consequences of internment.
My work aligns with recent studies 
by \cite{arellano-boverDisplacementDiversityMobility2022} 
and \cite{shoagCausalEffectPlace2016} 
in documenting upward mobility,
but it adds a crucial dimension by revealing that these gains were not uniform.
The concentration of effects among women
suggests that the forced break from pre-war community structures
and labor market constraints on the West Coast
may have paradoxically opened new avenues for economic participation in the post-war economy.
Although internees suffered lost out on their freedoms, property, and dignity,
these results provide a more complex understanding
of how individuals subjected to forced removal
can also adapt to their new environments.

\newpage
\singlespacing
\bibliography{internment_refs}

\newpage

\appendix

\section*{Appendix}

\input{../figures/piocrt_internment_map.tex}

\input{../figures/1940_map.tex}

\input{../figures/internee-age-plot.tex}

\input{../figures/pr_intern_plot.tex}

\input{../tables/cmp-cty_tbl}

\end{document}